Demographic Patterns in Toronto’s COVID-19 Cases: Are Elderly Males at Greater Risk?

### 2025-06-23 outputs/paper/paper.qmd
quick fix
anonymized & changed packages

---
title: "Exploring the Demographic Aspects of COVID-19 Cases in Toronto: Are the elderly males more susceptible to COVID-19?"
author: 
  - Amie Liu
thanks: "Code and data are available at:https://github.com/AmieLiu/COVID-19_Toronto_Demographic_Aspects_Analysis.git"
date: today
date-format: long
abstract: "Examining the age and gender patterns of COVID-19 cases in Toronto provides insights into the susceptibility of different demographic groups to the virus. This paper utilizes the dataset from Open Data Toronto, encompassing the period from January 22, 2020, to January 4, 2024. Contrary to the hypothesis that elderly males are more susceptible, the results reveal a pattern, with females aged 20-29 showing the highest susceptibility, exceeding 40,000 cases. This highlights the importance of understanding gender and age-specific patterns for effective public health interventions."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

The dataset 'COVID-19 Cases in Toronto'  [@covidCases] was utilized and obtained from 'opendatatoronto' library [@openDataToronto]. It comprises 412,122 records and 15 variables, including assigned ID, age group, neighborhood name, episode date, client gender, and more. The data cover the period from January 22, 2020, to January 4, 2024, and are structured in CSV file format.

>>>>

---
title: "Demographic Patterns in Toronto’s COVID-19 Cases: Are Elderly Males at Greater Risk?"
author: 
  - Lena Wang
thanks: "Code and data are available at: https://github.com/EveHughes/COVID-19_Toronto_Demographic_Aspects_Analysis"
date: today
date-format: long
abstract: "Examining the age and gender patterns of COVID-19 cases in Toronto provides insights into the susceptibility of different demographic groups to the virus. This paper utilizes the dataset from Open Data Toronto, encompassing the period from January 22, 2020, to January 4, 2024. Contrary to the hypothesis that elderly males are more susceptible, the results reveal a pattern, with females aged 20-29 showing the highest susceptibility, exceeding 40,000 cases. This highlights the importance of understanding gender and age-specific patterns for effective public health interventions."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

The dataset 'COVID-19 Cases in Toronto' [@covidCases] was utilized. It comprises 412,122 records and 15 variables, including assigned ID, age group, neighborhood name, episode date, client gender, and more. The data cover the period from January 22, 2020, to January 4, 2024, and are structured in CSV file format.
